Distributions

### 2022-01-12 Ch2_distributions/Ch2_Figures.Rmd
Changing the order of the figures.

@@

```{r fig.width=12, fig.height=4.5}
ptpl %>%
  drop_na(mpm) %>%
  filter(mpm != 0) %>%
  group_by(Bird_ID) %>%
  add_tally() %>%
  filter(n >= 30) -> nonzerompm

@@

nonzerompm %>%
  mutate(individual = paste0("B", Bird_ID),
         individual = factor(individual, levels = c("B1", "B3", "B5", "B7", "B13", "B19", "B22", "B28", "B49", "B84", "B30", "B29"))) %>% 
  group_by(individual, T_minutes) %>%
  count() %>%
  ggplot(aes(x = individual, y = n, fill = as.factor(T_minutes))) +
  geom_bar(stat = "identity") +
  theme_classic() +
  labs(x = "Individual bird tag",
       y = "Number of intervals recorded") +
  #scale_fill_viridis_d(option = "magma", direction = -1) +
  guides(fill = guide_legend(title = "Tracking interval\n in minutes")) +
  scale_fill_manual(values = met.brewer("Hiroshige", n = 14)) +
  theme(legend.position = "none") -> np_ints

@@

```{r eval=FALSE}
# Getting some data for the results
ptpl %>% group_by(burst) %>% add_tally(name = "burstn") %>% 
  dplyr::select(Bird_ID, burstn) %>% 
  filter(., burstn >=2) %>% 
  distinct() %>% #summary()
  ggplot(., aes(x = Bird_ID, y = burstn)) + 
  geom_boxplot()

>>>>

rawptpl <- ptpl

@@

```{r Figure1, fig.width=12, fig.height=4.5}
ptpl %>%
  drop_na(mpm) %>%
  filter(mpm != 0) %>%
  group_by(Bird_ID) %>%
  add_tally() %>%
  filter(n >= 30) -> nonzerompm

@@

nonzerompm %>%
  mutate(individual = paste0("B", Bird_ID),
         individual = factor(individual, levels = c("B1", "B3", "B5", "B7", "B13", "B19", "B22", "B28", "B49", "B84", "B30", "B29"))) %>% 
  group_by(individual, T_minutes) %>%
  count() %>%
  ggplot(aes(x = individual, y = n, fill = as.factor(T_minutes))) +
  geom_bar(stat = "identity") +
  theme_classic() +
  labs(x = "Individual bird tag",
       y = "Number of intervals recorded") +
  #scale_fill_viridis_d(option = "magma", direction = -1) +
  guides(fill = guide_legend(title = "Tracking interval\n in minutes")) +
  scale_fill_manual(values = met.brewer("Hiroshige", n = 14))

  #theme(legend.position = "none") -> np_ints

# This is the information on the bursts and number of relocations per individual

# ptpl %>% group_by(burst) %>% add_tally(name = "burstn") %>% 
#   dplyr::select(Bird_ID, burstn) %>% 
#   filter(., burstn >= 2) %>% 
#   distinct() %>% #summary()
#   #group_by(., Bird_ID) %>% count() %>% arrange(n)
#   ggplot(., aes(x = Bird_ID, y = burstn)) + 
#   geom_violin() +
#   geom_boxplot(width = 0.1)

ggsave("Ch2_distributions/Figures/Figure1.png")
```

```{r eval = FALSE}

# These are the plot and legend for the number of observations and intervals when we consider the data at the family level.

@@
